\theseminartitle \\ \small \thetitle

### 2021-09-28 tex/paper.tex
Added information about further structure of paper

	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper. More specifically, we want to evaluate the following questions:
	\begin{itemize}
		\item When do we need to benchmark software?
			\begin{itemize}
				\item Is it sufficient to benchmark releases?
				\item Do we need to benchmark every commit?
			\end{itemize}
		\item How do different continuous benchmarking approaches compare with respect to:
			\begin{itemize}
				\item Complexity of implementation?
				\item Reliably detecting performance changes?
				\item Reducing the amount of manual work required by the developer?
				\item Can we use this metric to compare arbitrary commits?
			\end{itemize}
	\end{itemize}

@@

@@

>>>>

	The main idea of the experiment that was created was to perform a benchmark on a series of versions of a specific open-source software to evaluate the methods and techniques described in this paper. More specifically, we want to evaluate the following questions:
	\begin{itemize}
		\item When do we need to benchmark software?
			\begin{itemize}
				\item Is it sufficient to benchmark releases?
				\item Do we need to benchmark every commit?
			\end{itemize}
		\item How do different continuous benchmarking approaches compare with respect to:
			\begin{itemize}
				\item Complexity of implementation?
				\item Reliably detecting performance changes?
				\item Reducing the amount of manual work required by the developer?
				\item Can we use this metric to compare arbitrary commits? TODO: Maybe remove
			\end{itemize}
	\end{itemize}

@@

	Based on these results, it can be seen that there is a significant performance regression between versions \textit{v1.8.0} and \textit{v1.8.1}. Therefore this commit range was also selected for further investigation of the individual commits.

@@

\subsection{Reviewing the Performance Benchmark Data}
-Baseline: E-Divisive Means
-Mention Performance Spike

\subsection{Comparing Methods to Detect Performance Changes}
-E-Divisive Means
-Jump Detection
-Trend Detection

Swiftness of detection w/ all three

\subsection{Conclusion}
benefits/problems of each detection method
